The ChEMBL database as Linked Open Data

### 2012-08-17 article.tex
Adding why RDF is important as a solution

For example, not all information in the databases has so far been annotated using
standard ontologies. That includes the activity types (``IC50'', ``EC50'', and ``Potency'' in ChEMBL), making it
still impossible to reason or group over similar activity types. For example,
the IC$_{50}$ and K$_i$ end point are closely related, but that is currently not
ontologically expressed. Similarly, measurement units are currently provided as
string literals, making it needlessly hard to compare concentrations in nM and mM.
If we further allow to make some assumptions, we can even search for activities
expressed in \mu g/ml with query concentration in nM.

>>>>

For example, not all information in the databases has so far been annotated using
standard ontologies. That includes the activity types (``IC50'', ``EC50'', and ``Potency'' in ChEMBL), making it
still impossible to reason or group over similar activity types. For example,
the IC$_{50}$ and K$_i$ end point are closely related, but that is currently not
ontologically expressed. Similarly, measurement units are currently provided as
string literals, making it needlessly hard to compare concentrations in nM and mM.
If we further allow to make some assumptions, we can even search for activities
expressed in $\mu$g/ml with query concentrations in nM. Without introducing machine-readable
semantics, such conversions are less easily automated.
